Continuously Monitoring the Evolution of Flask \& Python-Based Web Services

### 2018-04-09 evolution.tex
retitled
one more tiny detail

    \begin{figure}[h!]
      \centering
      \includegraphics[width=\linewidth]{utilization-evolution}
      \caption{Evolving Endpoint Utilization Across System Versions}
      \label{fig:mv-util}
    \end{figure}

@@

  With this view, several patterns could be visible on such a graph:
  \begin{itemize}

    \item Endpoints being deprecated. In the case study, \epFeedItems stops being used somewhere after the half of the presented timeline.

    \item Endpoints being introduced. In the case study, \epTopArticles appears soon after the half o the presented timeline.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=\linewidth]{time_per_user_per_version}
  \caption{This perspective shows that the evolution of response times for individual users (horizontal lines) across versions (the x-axis) for a given endpoint}
  \label{fig:tuv}
\end{figure}

>>>>

    \begin{figure}[h!]
      \centering
      \includegraphics[width=\linewidth]{utilization-evolution.pdf}
      \caption{Evolving Endpoint Utilization Across System Versions}
      \label{fig:mv-util}
    \end{figure}

@@

  Several patterns could be visible on such a graph:
  \begin{itemize}

    \item Endpoints being deprecated. In the case study, \epFeedItemsColor stops being used somewhere after the half of the presented timeline.

    \item Endpoints being introduced. In the case study, \epTopArticlesColor appears soon after the half o the presented timeline.

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.9\linewidth]{time_per_user_per_version}
  \caption{This perspective shows that the evolution of response times for individual users (horizontal lines) across versions (the x-axis) for a given endpoint}
  \label{fig:tuv}
\end{figure}
